\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-14 challenges.tex
more copyedit

In certain avenues of future work (Section~\ref{sec:future-linux}), remaining agnostic of most implementation details becomes less of an issue. For example, if we target Landslide to Linux, it is unlikely that core scheduler or interrupt-handling behaviour will change for as long as Landslide remains useful for finding bugs. In 15-410, however, repeated re-targetting is a necessity.

@@

\begin{itemize}
	\item {\bf Runqueues}: Does the kernel store the currently-running thread on the runqueue, or is it removed and stored separately?
	\item {\bf Mutexes}: When a thread blocks on a mutex, is it left on the runqueue in a yield-loop, or is it explicitly descheduled? In yield-looping mutexes, when do blocked threads become ``unblocked'', notionally? (This might happen before the blocked thread runs next.)
	\item {\bf Idling}: Does the kernel have an explicit idle thread, or is there an idle loop that runs on the stack of whatever thread was last running? Do explicit idle threads run their idle loop in userspace or in kernelspace?
	\item {\bf Thread Creation}: When a thread is newly forked, is it placed onto the runqueue for later, or is it context-switched to immediately? Do just-forked threads begin life through the usual context-switch-return path, or is there a special path for that?
	\item {\bf Test Lifecycle}: Even apart from running on a particular input that the user wishes to test, the kernel may need to perform extra work irrelevant to the test, such as initialisation (e.g. the bootup process) and housekeeping (e.g. cleaning up dead processes). Which parts of this work should be included or excluded in the test?
\end{itemize}

>>>>

% In certain avenues of future work (Section~\ref{sec:future-linux}), remaining agnostic of most implementation details becomes less of an issue. For example, if we target Landslide to Linux, it is unlikely that core scheduler or interrupt-handling behaviour will change for as long as Landslide remains useful for finding bugs. In 15-410, however, repeated re-targetting is a necessity.

@@

\begin{itemize}
	\item {\bf Runqueues}: Does the kernel store the currently-running thread on the runqueue, or is it ``checked out'' while running and stored separately?
	\item {\bf Mutexes}: When a thread blocks on a mutex, is it left on the runqueue in a yield loop, or is it explicitly descheduled (e.g., moved from the runqueue to another queue)? In yield-looping mutexes, when do blocked threads become ``unblocked'', notionally? (This might happen before the blocked thread runs next.)
	\item {\bf Idling}: Does the kernel have an explicit idle thread, or is there an idle loop that runs on the stack of whatever thread was last running? Do explicit idle threads run their idle loop in userspace or in kernelspace?
	\item {\bf Thread Creation}: When a thread is newly forked, is it placed onto the runqueue for later, or is it context-switched to immediately? Do just-forked threads begin life through the usual context-switch-return path, or is there a special path for that?
	\item {\bf Test Lifecycle}: Apart from running on a particular input that the user wishes to test, the kernel may need to perform extra work irrelevant to the test, such as initialisation (e.g., the bootup process) and housekeeping (e.g., cleaning up dead processes). Which parts of this work should be included in or excluded from the test?
\end{itemize}

### 2012-05-14 related.tex
more copyedit

Landslide distinguishes itself from related systematic testing tools in its field as more of an exploratory work, presenting techniques to make systematic testing compatible with kernel-level code; less so as a development on the core testing approach itself.

>>>>

Landslide is distinguished from related systematic testing tools in its field as more of an exploratory work, presenting techniques to make systematic testing compatible with kernel-level code; less so as a development on the core testing approach itself.

### 2012-05-14 thesis.tex
add model section
more copyedit

\setcounter{changebargrey}{35}
\newcommand\revision[1]{\begin{samepage}\cbstart#1\cbend\end{samepage}}
%\newcommand\revision[1]{#1}

@@

We present Landslide, a systematic exploration tool for finding races in kernels.
Landslide targets Pebbles, the kernel specification that students implement in the undergraduate Operating Systems course at Carnegie Mellon University (15-410).
We discuss the techniques Landslide uses to address the general challenges of kernel-level concurrency, and we evaluate its effectiveness and usability as a debugging aid.
We show that our techniques make systematic testing in kernel-space feasible, and that Landslide is a useful tool for doing so in the context of 15-410.
\end{abstract}

@@

We present Landslide,\footnote{
Landslide {\em (n)}: a phenomenon which demonstrates that Pebbles are not as stable as you might think.}
a tool for applying systematic race detection techniques in to kernel-level code.
It is geared towards kernels that implement the Pebbles specification, the main project in Operating System Design and Implementation (15-410) at CMU, and implemented as a module for Wind River Simics\textsuperscript{\texttrademark}, the x86 simulator that students use to run their Pebbles kernels.
During execution of a kernel, Landslide records important actions performed by the kernel, attempts to decide at which points in the kernel's execution a preemption will be most likely to expose a bug, and then exercises all possible interleavings of kernel threads around such points.
When Landslide finds a bug (predicted by a set of common checks and heuristics), it stops execution and prints information about the sequence of interleavings that exposed the bug.

>>>>

\setcounter{changebargrey}{35}
%\newcommand\revision[1]{\begin{samepage}\cbstart#1\cbend\end{samepage}}
\newcommand\revision[1]{\cbstart#1\cbend}
%\newcommand\revision[1]{#1}

@@

We present Landslide, a systematic exploration tool for finding races in kernels.
Landslide targets Pebbles, the kernel specification that students implement in the undergraduate Operating Systems course at Carnegie Mellon University (15-410).
We discuss the techniques Landslide uses to address the general challenges of kernel-level concurrency, and we evaluate its effectiveness and usability as a debugging aid.
We show that our techniques make systematic testing in kernel-space feasible and that Landslide is a useful tool for doing so in the context of 15-410.
\end{abstract}

@@

We present Landslide,\footnote{
Landslide {\em (n)}: a phenomenon which demonstrates that Pebbles are not as stable as you might think.}
a tool for applying systematic race detection techniques in to kernel-level code.
It is geared towards kernels that implement the Pebbles specification, the main project in Operating System Design and Implementation (15-410) at CMU, and is implemented as a module for Wind River Simics\textsuperscript{\texttrademark}\cite{simics}, the x86 simulator that students use to run their Pebbles kernels.
During execution of a kernel, Landslide records important actions performed by the kernel, attempts to decide at which points in the kernel's execution a preemption will be most likely to expose a bug, and then exercises all possible interleavings of kernel threads around such points.
When Landslide finds a bug (predicted by a set of common checks and heuristics), it stops execution and prints information about the sequence of interleavings that exposed the bug.
